### 2025-08-22 sec/related-work.tex
Bib fixes.

Recent advances in interpretable language understanding, highlighting the shift from fine-tuning to
prompt-based learning in NLP and presenting research on improving the transparency of neural models through
interpretable classifiers, uncertainty analysis, and explainable systems. \cite{Yulan_2023}

@@

For example quantity extraction~\cite{bolucu-etal-2023-investigating}, scientific fact-checking
\cite{abu-ahmad-etal-2025-climatecheck-shared}.

@@

\cite{perera22,bond25,psallidas18smoke}

>>>>

Recent advances in interpretable language understanding, highlighting the shift from fine-tuning to
prompt-based learning in NLP and presenting research on improving the transparency of neural models through
interpretable classifiers, uncertainty analysis, and explainable systems \cite{yulan23}.

@@

For example quantity extraction~\cite{bolucu23}, scientific fact-checking
\cite{abu-ahmad25}.

@@

\cite{atkey25,perera22,bond25,psallidas18smoke}
